Prediction of functional markers of mass cytometry data via deep learning

### 2019-02-07 revision/answers2reviewers.md

# Answers to reviewers

We thank the reviewers for such insightful comments which had certainly improved the manuscript greatly.

## From reviewer 1

1. "For the deep learning framework, there is not too much novelty. In my opinion, the paper is a pioneer of practitioner of the deep learning in their specific research area."
We agree! Neural networks are widely studied models that have been applied to a variety of real-life datasets. We are not proposing new model developments for the area of neural network; we are applying existing neural network tools to the case of flow cytometry area which has not fully adopted the deep learning schemes yet.
We added these points in the introduction/discussion

### 2019-02-07 revision/latex_template/author.tex
finished resubmission

Recently, deep learning models are revolutionizing the fields of
precision medicine, data mining, astronomy, human-computer
interactions, among many others, by becoming a major discovery force
in science due to the unprecedented accuracy in prediction.
\claudia{Moreover}{However}, \claudia{}{despite} deep learning
approaches \claudia{have shown}{showing} accurate performance on
genomics and biomedical
applications\cite{Ciresan2013,Denas2013,Fakoor2013,Leung2014,CruzRoa2014,Li2017,Mobadersany2018},
\claudia{}{the CyTOF community has not fully adopted these
  approaches.}  \claudia{Furthermore}{In fact, it turns out that}
CyTOF data is perfectly suited for deep learning methods.  On one
side, identify markers define a cell type (e.g., B cell, T cell,
monocytes, MSC), and on the other side, expressions of functional
markers identify the cell's activity (e.g., quiescent, secreting
cytokines, proliferating, apoptosis). Since CyTOF technology allows
for the simultaneous measurement of a large number of protein markers,
most CyTOF studies measure both identity markers and functional
markers, providing data for supervised learning tools, like neural
networks.  In addition, each CyTOF run typically collects data on
$10^6$ cells, creating an ideal large dataset in which the number of
samples (cells) is orders of magnitude larger than the number of
variables (markers). Deep learning methods are particularly suited for
this type of big data.

>>>>

Recently, deep learning models are revolutionizing the fields of
precision medicine, data mining, astronomy, human-computer
interactions, among many others, by becoming a major discovery force
in science due to the unprecedented accuracy in prediction.
\claudia{Moreover}{However}, \claudia{}{despite} deep learning
approaches \claudia{have shown}{showing} accurate performance on
genomics and biomedical
applications\cite{Ciresan2013,Denas2013,Fakoor2013,Leung2014,CruzRoa2014,Li2017,Mobadersany2018},
\claudia{}{the CyTOF community has not fully adopted these
  methods yet.}  \claudia{Furthermore}{In fact, it turns out that}
CyTOF data is perfectly suited for deep learning methods.  On one
side, identify markers define a cell type (e.g., B cell, T cell,
monocytes, MSC), and on the other side, expressions of functional
markers identify the cell's activity (e.g., quiescent, secreting
cytokines, proliferating, apoptosis). Since CyTOF technology allows
for the simultaneous measurement of a large number of protein markers,
most CyTOF studies measure both identity markers and functional
markers, providing data for supervised learning tools, like neural
networks.  In addition, each CyTOF run typically collects data on
$10^6$ cells, creating an ideal large dataset in which the number of
samples (cells) is orders of magnitude larger than the number of
variables (markers). Deep learning methods are particularly suited for
this type of big data.
